### 2018-04-08 analysis_code/agents_table.Rmd
updates

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_exp_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

@@

concise_alg_rep <- function(alg) {
  if (alg == "ThompsonSampling") {
    return("TS")
  } else if (alg == "DynamicEpsilonGreedy") {
    return("DEG")
  } else if (alg == "DynamicGreedy") {
    return("DG")
  }
}

concise_agent_rep <- function(agent_alg) {
  if (agent_alg == "HardMax") {
    return("HM")
  } else if (agent_alg == "HardMaxWithRandom") {
    return("HMR")
  } else if (agent_alg == "SoftMax") {
    return("SM")
  }
}

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_large_horizon_3_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000, 15000)
priors <- as.list(unique(dat['Prior']))$Prior

@@

concise_alg_rep <- function(alg) {
  if (alg == "ThompsonSampling") {
    return("TS")
  } else if (alg == "DynamicEpsilonGreedy") {
    return("BEG")
  } else if (alg == "DynamicGreedy") {
    return("BG")
  }
}

concise_agent_rep <- function(agent_alg) {
  if (agent_alg == "HardMax") {
    return("EU")
  } else if (agent_alg == "HardMaxWithRandom") {
    return("Noisy EU")
  } else if (agent_alg == "SoftMax") {
    return("Logit")
  }
}

### 2018-04-08 analysis_code/tournament_table.Rmd
updates

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/full_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_test_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- algs
        rownames(results) <- algs
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/full_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
alg_names <- c("Thompson Sampling", "Bayesian Epsilon Greedy", "Bayesian Greedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- alg_names
        rownames(results) <- alg_names
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }
